---
title: "R MidTerm"
output: html_notebook
---

QUESTION 1

Complete the following questions, then submit this R Notebook with your work on Camino.

Load the data in the file "fillna.txt", replace the NA's with "unknown" and save to a new file called "cleaned.txt"
```{r}
## Student code goes here

## Student code goes here
```

QUESTION 2

Load the table fillna.txt and 
a) create a vector of NA counts by column
b) create a vector of NA counts by row

```{r}
## Student code goes here

## Student code goes here
```

QUESTION 3

Load the mtcars dataset, and show the structure of the table.

```{r}
## Student code goes here



## Student code goes here
```


QUESTION 4
Load the airquality dataset and show the first 7 rows. (PART A)

```{r}
## Student code goes here



## Student code goes here
```


... and show the last 4 rows of data (PART B)

```{r}
## Student code goes here



## Student code goes here
```


Show data for the month of May (PART C)

```{r}
## Student code goes here



## Student code goes here
```

QUESTION 5

Load the Orange dataset, and perform the following analyses. Organize your work and present your answers with separate R Notebook cells.

a. Do a simple scatterplot of Age vs circumference.
b. Make a stripchart of age
c. Change the graph from part (a) as follows:
1. Use red dots
2. Label the graph from exercise one as:
-- Title = Tree Age vs circumference
-- X axis = age
-- Y axis = circumference of tree


** STUDENT CODE CELLS SHOULD GO HERE. Create your own cells! **

QUESTION 6
Using the Orange Dataset again, create a graph that shows the distribution of values of the circumference column

```{r}
## Student code goes here

## Student code goes here
```


