---
title: "R MidTerm"
output: html_notebook
---

Complete the following questions, then submit this R Notebook with your work on Camino.

QUESTION 1

Load the dataset arquality and show days im June when temperature was higher then 70..
```{r}
## Student code goes here

## Student code goes here
```

QUESTION 2

Load the table fillna.txt and 
a) create a vector of NA counts by column
b) create a vector of NA counts by row

```{r}
## Student code goes here

## Student code goes here
```

QUESTION 3

Load the orange dataset, and show the structure of the table.

```{r}
## Student code goes here



## Student code goes here
```


QUESTION 4
Load the ggplot2 library. Next, load the 'diamonds' dataset. (Note you may use dplyr for these questions, but do not need to.)

Plot the diamonds' clarity by price (PART A)

```{r}
## Student code goes here



## Student code goes here
```


Show the last 4 rows of data (PART B)

```{r}
## Student code goes here



## Student code goes here
```


Show the median price  (PART C)

```{r}
## Student code goes here



## Student code goes here
```

QUESTION 5

Load the Orange dataset, and perform the following analyses. Organize your work and present your answers with separate R Notebook cells.

a. Do a simple scatterplot of Age vs circumference.
b. Make a stripchart of age
c. Change the graph from part (a) as follows:
1. Use orange dots
2. Label the graph exercise one as:
-- Title = Tree Age vs circumference
-- X axis = Age
-- Y axis = circumference of Tree


** STUDENT CODE CELLS SHOULD GO HERE. Create your own cells! **

QUESTION 6
Using the Diamond dataset again, create a graph that shows the distribution of values for the diamond prices column. 

```{r}
## Student code goes here

## Student code goes here
```



